Sheafification in HoTT

### 2015-01-12 paper/sheaf_lics.tex
paper

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]{\ar@<2pt>[#1]\ar@<-2pt>[#1]}
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$C(f) := \cdots
    X \times_Y X \times_Y X
   \underset{\longrightarrow}{\stackrel{\longrightarrow}{\longrightarrow}}
   X \times_Y X 
\stackrel{\longrightarrow}{\longrightarrow} X$$
with canonical projections.
\end{defi}

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\cdots \overline{\Delta_3} \underset{\longrightarrow}{\stackrel{\longrightarrow}{\longrightarrow}}
   \overline{\Delta_2}
\stackrel{\longrightarrow}{\longrightarrow} \overline{\Delta_1},$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}
\begin{proof}
  As $\mu_T$ is an embedding, we know by Giraud axiom that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.

@@

@@

\bibitem[RS13]{sets_in_hott}
Egbert Rijke and Bas Spitters.
\newblock Sets in homotopy type theory.
\newblock 2013.

@@

\bibitem[lumsdaine]{lumsdaine}
Lumsdaine
\newblock{Diagrams and limits}

>>>>

\usepackage{enumerate}
\usepackage{wasysym}
\usepackage[all]{xy}
\def\dar[#1]{\ar@<2pt>[#1]\ar@<-2pt>[#1]}
\def\tar[#1]{\ar@<2pt>[#1]\ar@<0pt>[#1]\ar@<-2pt>[#1]}
\DeclareMathOperator{\Type}{Type}
\DeclareMathOperator{\HProp}{HProp}
\DeclareMathOperator{\nat}{nat}
\DeclareMathOperator{\Unit}{Unit}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Contr}{Contr}
\newcommand{\modal}{\ensuremath{\ocircle}}

@@

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$\xymatrix{
    C(f) := \cdots~ X \times_Y X \times_Y X \tar[r] & X \times_Y X \dar[r] & X
  }$$
with canonical projections.
\end{defi}

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\xymatrix{ 
    \cdots \overline{\Delta_3} \tar[r] & \overline{\Delta_2} \dar[r] &
    \overline{\Delta_1}
  }$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}
\begin{proof}
  As $\mu_T$ is an embedding, we know by Giraud axiom that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.

@@

Let $T:\Type_{n+1}$ such that $\star X$ is contractible. Let
$x,y:T$. We want to show that $\star (x=y)$ is contractible.

As $\star T$ is contractible, we have a center $u_0 : T \to
\Type_n^\modal$ with an hypothesis $H_0 :  \lnot\lnot\left\| \sum_{a:X} 
            (\lambda t,~\modal (a=t)) = u_0\right\|$, and a
          contractibility condition $c : \prod_{t:\star T} x = (u_0,H_0)$.
As $\Contr (\star (x=y))$ is a $\HProp$-sheaf, we can change $H_0$
into a $a:T$ and a proof $u_0 = (\lambda t,~\modal (a=t))$.
Finally, $c$ type becomes $\prod_{v:\star T} v_1 =  (\lambda t,~\modal (a=t))$.

@@

\bibitem[RS13]{sets_in_hott}
Egbert Rijke and Bas Spitters.
\newblock {\em Sets in homotopy type theory}.
\newblock 2013.

@@

\bibitem[lumsdaine]{lumsdaine}
Peter LeFanu Lumsdaine, Jeremy Avigad and Chris Kapulkin
\newblock{\em Homotopy limits in type theory}
